---
title: "Meta-analysis: Relationship between procedural learning and language and literacy"
author: "Cátia Margarida Oliveira[^1], Marianna E. Hayiou-Thomas, Lisa Henderson; University of York"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  markdown: 
    wrap: 72
#bibliography: references.bib
---

<br> <br> This file is licensed under the terms and conditions of the
CC-BY 4.0 INTERNATIONAL\
for details on the license, see\
<http://creativecommons.org/licenses/by/4.0/>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8", 
                      filename = 'render_toc.R')
```

# Import functions

```{r}
source("utils.R")
```

# Import libraries

```{r echo = T,warning=FALSE,message=FALSE}

MAc <- "https://cran.r-project.org/src/contrib/Archive/MAc/MAc_1.1.tar.gz"
install.packages(MAc, repos=NULL, type="source")

listOfPackages <- c("readxl", "rmarkdown","robumeta","SciViews","PublicationBias","clubSandwich",
                    "metafor","tidyverse","readxl", "stats","dplyr", "here", "stargazer", "gridExtra", "purrr", "cowplot")
ipak(listOfPackages)

```

# Data analysis

To know more about Robust Variance Estimation Meta-Analysis see
[@fisher2015; @hedges2010; @tanner-smith2014]

```{r echo = T}
# Read in file
Dat <- read.csv(here("meta-analysis_data_analysis.csv"))

#transform correlations into Fish\er Z and compute variance for effect sizes
Dat <- escalc(measure = "ZCOR", ri = Cor, ni = N, data = Dat)

#Calculate standard error - Borenstein et al. (2009) 
Dat$sei <- sqrt(Dat$vi) 

#subset data - all entries except for RAN
Data <- subset(Dat, Variable == "Literacy"|Variable == "Language")
RAN <- subset(Dat, Component == "RAN")

```

# Descriptives

```{r echo = TRUE}

Desc <- Data %>% group_by(Study, Group) %>% summarise(N = mean(N), Age = round(mean(Age),2), Authors = Authors[1], Year = Year[1], SRT = Seq_type[1], sequence = Seq_complexity[1])

# Add number of participants and age to Earle & Ullman (2021)

Desc$N[13] <- 79 
Desc$N[12] <- 21
Desc$Age[13] <- 20.49
Desc$Age[12] <- 20.52

Desc

#write.csv(Desc, "desc.MA.csv")
```

Total number of participants: `r sum(Desc$N)` <br> Participants age
range: `r round(range(Desc$Age),2)`, M = `r round(mean(Desc$Age),2)`, SD
= `r round(sd(Desc$Age),2)`

```{r echo = TRUE}
#subdivide data into language and literacy measures
Data_language <- subset(Data, Variable == "Language")
Data_literacy <- subset(Data, Variable == "Literacy")

#subdivide data into language and literacy components
Data_grammar <- subset(Data, Component == "Grammar")
Data_phonology <- subset(Data, Component == "Phonology")
Data_vocabulary <- subset(Data, Component == "Vocabulary")
Data_reading <- subset(Data, Component == "Reading")
Data_spelling <- subset(Data, Component == "Spelling")

#Preprocessing

Data$Trial_no <- scale(Data$Trial_no)
Data$Age <- scale(Data$Age)
```

# Overall model with synthesised effect sizes

## Model with synthesised effect sizes for correlation of .5 (default)

The default imputed correlation between within-study effect sizes is set
at .50 (Wampold et al., 1997)

```{r echo = T}

study.details <- Data %>%
  dplyr::select("Study", "Authors", "Year") %>%
  dplyr::rename(id = Study) %>% group_by(id) %>%
  summarise(id = id[1], Study = Authors[1], Year = Year[1])

# combine effect sizes
agg.Data.dat <- MAc::agg(id = Study, r = Cor, n = N, cor = .5, mod=NULL, data = Data)
agg.Data.dat  <- escalc(measure = "ZCOR", ri = r, ni = n, data = agg.Data.dat)

agg.Data.dat <- as.data.frame(list(agg.Data.dat, study.details) %>% reduce(right_join, by = c("id"))) 

### fit fixed-effects model
res <- rma(yi, vi, data= agg.Data.dat)
print(res)

```

### Forest plot

```{r echo = T}

# back-transform the results to correlations and obtain the prediction interval
predict(res, transf=transf.ztor, digits=2)

# draw forest plot
forest(res, header=TRUE, atransf=transf.ztor, order="obs", xlim=c(-1.2, .9),
       at=transf.rtoz(seq(-0.6,0.6,by=0.1)), refline=coef(res), ilab=cbind(agg.Data.dat$Study, agg.Data.dat$Year),  ilab.xpos=c(-1,-.8), cex=.75)
text(c(-1.2, .9), c("Author(s)", "Year"))

### add text with Q-value, dfs, p-value, and I^2 statistic
text(-16, -1, pos=4, cex=0.75, bquote(paste("RE Model (Q = ",
     .(formatC(res$QE, digits=2, format="f")), ", df = ", .(res$k - res$p),
     ", p = ", .(formatC(res$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(res$I2, digits=1, format="f")), "%)")))

```

## Sensitivity analysis - Model with synthesised effect sizes for various correlation sizes

```{r echo = T}

#combine effect sizes with different correlation sizes

compute_rma <- function(cor, Study, Cor, N, Data) {
  d <- MAc::agg(id = Study, r = Cor, n = N, cor = cor, mod=NULL, data = Data)
  d <- escalc(measure = "ZCOR", ri = r, ni = n, data = d)
  rma(yi, vi, data= d, measure="OR", method="REML")
}

results = list()
for (cor in  seq(.1, 1,.2))  {
    results[[as.character(cor)]] = compute_rma(cor, Study, Cor, N, Data)
  }

print(results)
```

## Diagnostic {.tabset}

### Funnel Plots

```{r echo = T}
### set up 2x2 array for plotting
par(mfrow=c(2,2))

### draw funnel plots
funnel(res, main="Standard Error")
funnel(res, yaxis="vi", main="Sampling Variance")
funnel(res, yaxis="seinv", main="Inverse Standard Error")
funnel(res, yaxis="vinv", main="Inverse Sampling Variance")
dev.off()

### funnel plot
funnel(res)

### create contour enhanced funnel plot (with funnel centered at 0)
funnel(res, level=c(90, 95, 99), shade=c("white", "orange", "red"), refline=0, legend = TRUE)

```

### Egger's regression test/ PET-PEESE procedure

```{r echo = T}
#Tests for bias
regtest(res) # PET
regtest(res, predictor="vi") # PEESE
```

### Rank correlation test

```{r echo = T}
#Tests for bias
ranktest(res, exact = FALSE)
```

Both ranktest and Egger's regression test do not test directly for
publication bias. Instead, they indicate whether there's evidence that
the funnel plot is asymmetric, which may occur due to publication bias,
but not exclusively. According to these results there's no evidence that
there is plot asymmetry.

### Outlier/influential points detection

```{r echo = T, out.width="50%"}
par("mar")

### calculate influence diagnostics
inf <- influence(res)
 
### plot the influence diagnostics
plot(inf)
```

Neither Egger's regression test (p = .192) or the Rank correlation test
(p = .838) was statistically significant so there's no evidence of
publication bias according to these tests. Study 27 is identified as
outlier/influential

# Overall model with dependency

```{r echo = T}
# Overall model with dependencies: general model

intercept.model <- robu(formula = yi ~ 1, data = Data,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(intercept.model)
sensitivity(intercept.model)
```

## Forest plot

```{r echo = T}

forest.robu(intercept.model, es.lab = "Variable", study.lab = "Study")

```

## Diagnostic

### Egger's regression test/ PET-PEESE procedure

```{r echo = T}

# with un-corrected ES (PET) - use standard error as predictor
PET <- robu(formula = yi ~ sei, data = Data,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(PET)

# with un-corrected ES (PEESE) - use variance as predictor
PEESE <- robu(formula = yi ~ vi, data = Data,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(PEESE)

```

## Moderators {.tabset}

### Overall Model with Variable - Language vs Literacy

```{r echo = T}
#without intercept
Var.model<- robu(formula = yi ~ factor(Variable)-1, data = Data, studynum = Study, var.eff.size = vi,  rho = .8, small = TRUE)
print(Var.model)
sensitivity(Var.model)

#run pairwise comparisons between variables
Wald_test(Var.model, constraints = constrain_pairwise(1:2), vcov = "CR2", tidy = TRUE)

```

### Overall Model with Group

```{r echo = T}

stats::addmargins(table(Data$Variable, Data$Group))

#Set Group as factor
Data$Group <- as.factor(Data$Group)

#without intercept
Group.model<- robu(formula = yi ~ 0 + Group, data = Data, studynum = Study, var.eff.size = vi,  rho = .8, small = TRUE)
print(Group.model)
sensitivity(Group.model)

#test overall group effect
Wald_test(Group.model, constraints = matrix(c(1,0,0,0,1,0,0,0,1),3,3), vcov = "CR2")

#run pairwise comparisons between groups
Wald_test(Group.model, constraints = constrain_pairwise(1:3), vcov = "CR2", tidy = TRUE)

```

### Overall Model with Age

```{r echo = T}

#without intercept

Age.model<- robu(formula = yi ~ Age, data = Data, studynum = Study, var.eff.size = vi,  rho = .8, small = TRUE)
print(Age.model)

sensitivity(Age.model)

```

# Modelling - Language

## Model with synthesised effect sizes

```{r echo = T}

agg.Data.lang <- MAc::agg(id = Study, r = Cor, n = N, cor = .5, mod=NULL, data = Data_language)
agg.Data.lang  <- escalc(measure = "ZCOR", ri = r, ni = n, data = agg.Data.lang)

#add details
agg.Data.lang <- as.data.frame(list(agg.Data.lang, study.details) %>% reduce(left_join, by = c("id"))) 

### fit fixed-effects model
res_lang <- rma(yi, vi, data= agg.Data.lang)
print(res_lang)

predict(res_lang, digits=3, transf=transf.ztor)

```

## Sensitivity analysis - Model with synthesised effect sizes

```{r echo = T}

#combine effect sizes with different correlation sizes

compute_rma <- function(cor, Study, Cor, N, Data) {
  d <- MAc::agg(id = Study, r = Cor, n = N, cor = cor, mod=NULL, data = Data_language)
  d <- escalc(measure = "ZCOR", ri = r, ni = n, data = d)
  rma(yi, vi, data= d, measure="OR", method="REML")
}

results = list()
for (cor in  seq(.1, 1,.2))  {
    results[[as.character(cor)]] = compute_rma(cor, Study, Cor, N, Data)
  }

print(results)
```

## Forest plot

```{r echo = T}
# back-transform the results to correlations and obtain the prediction interval
predict(res_lang, transf=transf.ztor, digits=2)

# draw forest plot
forest(res_lang, header=TRUE, atransf=transf.ztor, order="obs", xlim=c(-1.2, .9),
       at=transf.rtoz(seq(-0.6,0.6,by=0.1)), refline=coef(res_lang), ilab=cbind(agg.Data.lang$Study, agg.Data.lang$Year),  ilab.xpos=c(-1,-.8), cex=.75)
text(c(-1.2, .9), c("Author(s)", "Year"))

dev.copy(jpeg,filename="forest.lang.jpg");
dev.off ();
```

## Diagnostics {.tabset}

### Funnel plots

```{r echo = T}
### set up 2x2 array for plotting
par(mfrow=c(2,2))

### draw funnel plots
funnel(res_lang, main="Standard Error")
funnel(res_lang, yaxis="vi", main="Sampling Variance")
funnel(res_lang, yaxis="seinv", main="Inverse Standard Error")
funnel(res, yaxis="vinv", main="Inverse Sampling Variance")
dev.off()

```

```{r contour plot}
### funnel plot
png("funnel.lang.png",bg = "white", width = 1024, height = 768)
funnel(res_lang)
dev.off()

### create contour enhanced funnel plot (with funnel centered at 0)
png("funnel.lang.colour.png",bg = "white", width = 1024, height = 768)
funnel(res_lang, level=c(90, 95, 99), shade=c("white", "orange", "red"), refline=0, legend=TRUE)
dev.off()
```

### PET-PEESE

```{r echo = T}
#Tests for bias
regtest(res_lang) # PET
regtest(res_lang, predictor="vi") # PEESE
```

### Outlier/influential points detection

```{r echo = T}

### calculate influence diagnostics
inf_lang <- influence(res_lang)
 
### plot the influence diagnostics
plot(inf_lang)
```

## Language Model with dependencies

```{r echo = T}
# Overall model with dependencies: general model

intercept.lang.model <- robu(formula = yi ~ 1, data = Data_language,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(intercept.lang.model)
sensitivity(intercept.lang.model)
```

### Forest plot

```{r echo = T}
pdf(file = "forestplot_lang.pdf", width = 20, height = 42, pointsize = 5)

forest.robu(intercept.lang.model, es.lab = "Component", study.lab = "Study", "Effect Size" = yi)

dev.off()
```

### Diagnostic

#### Egger's regression test/ PET-PEESE procedure

```{r echo = T}

# with un-corrected ES (PET) - use standard error as predictor
PET_lang <- robu(formula = yi ~ sei, data = Data_language,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(PET_lang)

# with un-corrected ES (PEESE) - use variance as predictor
PEESE_lang <- robu(formula = yi ~ vi, data = Data_language,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(PEESE_lang)

```

### Moderators {.tabset}

#### Language model - age as predictor

```{r echo = T}
# Overall model with dependencies: general model

lang.age <- robu(formula = yi ~ Age, data = Data_language,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lang.age)

sensitivity(lang.age)

```

#### Language model - group as predictor

```{r echo = T}
# Overall model with dependencies: general model

Data_language$Group <- as.factor(Data_language$Group)
Data_language$Group <- relevel(Data_language$Group, ref= "TD")

lang.group <- robu(formula = yi ~ as.factor(Group)-1, data = Data_language,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lang.group)
sensitivity(lang.group)

#test overall group effect (i.e. do estimates differ from zero)
Wald_test(lang.group, constraints = matrix(c(1,0,0,0,1,0,0,0,1),3,3), vcov = "CR2", tidy = TRUE)

#run comparisons between groups (i.e. do estimates differ from each other)
V_lang.group <- vcovCR(lang.group, type = "CR2")
Wald_test(lang.group, constraints = constrain_equal(1:3), vcov = V_lang.group)

```

#### Language model - component as predictor

```{r echo = T}
# Overall model with dependencies: general model
df <- subset(Data_language, (Component %in% c("Grammar","Vocabulary","Phonology")))

lang.component <- robu(formula = yi ~ 0 + Component, data = df,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lang.component)

sensitivity(lang.component)

#test overall component effect (i.e. do estimates differ from zero)
Wald_test(lang.component, constraints = matrix(c(1,0,0,0,1,0,0,0,1),3,3), vcov = "CR2",tidy = TRUE)

#run comparisons between components (i.e. do estimates differ from each other)
V_lang.component <- vcovCR(lang.component, type = "CR2")
Wald_test(lang.component, constraints = constrain_equal(1:3), vcov = V_lang.component)
```

#### Language model - Sequence complexity

```{r echo = T}
# Overall model with dependencies: general model )

lang.seq.complexity <- robu(formula = yi ~ as.factor(Seq_complexity)-1, data = Data_language[Data_language$Seq_complexity == "FOC" | Data_language$Seq_complexity == "SOC", ],
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lang.seq.complexity)
sensitivity(lang.seq.complexity)

#run comparisons between groups
V_seq.complexity <- vcovCR(lang.seq.complexity, type = "CR2")

#test overall seq.complexity effect (i.e. do estimates differ from zero)
Wald_test(lang.seq.complexity, constraints = constrain_zero(1:2), vcov = V_seq.complexity)

#run comparisons between seq.complexity (i.e. do estimates differ from each other)
Wald_test(lang.seq.complexity, constraints = constrain_equal(1:2), vcov = V_seq.complexity)
```

#### Language model - Session

```{r echo = T}
# Overall model with dependencies: general model

table(Data_language$Time)

# The effect of session was only analysed on studies that looked at session 1,2,3 in isolation as the other contrasts were only based on single studies and thus not reliable

lang.session<- robu(formula = yi ~ as.factor(Time)-1, data = Data_language[Data_language$Time %in% c(1,2,3), ],
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)

print(lang.session)
sensitivity(lang.session)

#check overall session effect (i.e. do estimates differ from zero)
Wald_test(lang.session, constraints = matrix(c(1,0,0, 0,1,0, 0,0,1),3,3), vcov = "CR2", tidy = TRUE)

#run comparisons between groups (i.e. do estimates differ from each other)
V_lang.session <- vcovCR(lang.session, type = "CR2")
Wald_test(lang.session, constraints = constrain_equal(1:3), vcov = V_lang.session)
```

#### Language model - Number of trials

```{r echo = T}
# Overall model with dependencies: general model

lang.trials <- robu(formula = yi ~ Trial_no, data = Data_language,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lang.trials)
#sensitivity(lang.trials)

```

#### Language model - Type of sequence

```{r echo = T}
# Overall model with dependencies: general model

lang.seq.type <- robu(formula = yi ~ as.factor(Seq_type)-1, data = Data_language,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lang.seq.type)
sensitivity(lang.seq.type)

#test overall SRT type effect (i.e. do estimates differ from zero)
Wald_test(lang.seq.type, constraints = matrix(c(1,0,0,0,1,0,0,0,1),3,3), vcov = "CR2", tidy = TRUE)

#run comparisons between groups (i.e. do estimates differ from each other)
V_lang.seq.type <- vcovCR(lang.seq.type, type = "CR2")
Wald_test(lang.seq.type, constraints = constrain_equal(1:3), vcov = V_lang.seq.type)
```

### Language components - Comparison between groups {.tabset}

#### Grammar model - group as predictor

```{r echo = T}

table(Data_grammar$Group, Data_grammar$Component)

grammar.model <- robu(formula = yi ~ 0 + Group, data = Data_grammar,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(grammar.model)

sensitivity(grammar.model)

#test overall component effect (i.e. do estimates differ from zero)
Wald_test(grammar.model, constraints = matrix(c(1,0,0,0,1,0,0,0,1),3,3), vcov = "CR2",tidy = TRUE)

#run comparisons between groups (i.e. do estimates differ from each other)
V_grammar.model <- vcovCR(grammar.model, type = "CR2")
Wald_test(grammar.model, constraints = constrain_pairwise(1:3), vcov = V_grammar.model)

```


#### Vocabulary model - group as predictor

```{r echo = T}

table(Data_vocabulary$Group, Data_vocabulary$Component)

vocabulary.model <- robu(formula = yi ~ 0 + Group, data = Data_vocabulary[Data_vocabulary$Group != 'DD',],
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(vocabulary.model)

sensitivity(vocabulary.model)

#test overall component effect (i.e. do estimates differ from zero)
V_vocabulary.model <- vcovCR(vocabulary.model, type = "CR2")
Wald_test(vocabulary.model, constraints = constrain_zero(1:2), vcov = V_vocabulary.model)

#run comparisons between groups (i.e. do estimates differ from each other)
V_vocabulary.model <- vcovCR(vocabulary.model, type = "CR2")
Wald_test(vocabulary.model, constraints = constrain_equal(1:2), vcov = V_vocabulary.model)
```

#### Phonology model - group as predictor

```{r echo = T}

table(Data_phonology$Group, Data_phonology$Component)
phonology.model <- robu(formula = yi ~ 0 + Group, data = Data_phonology,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(phonology.model)
sensitivity(phonology.model)

#test overall component effect (i.e. do estimates differ from zero)
V_phonology.model <- vcovCR(phonology.model, type = "CR2")
Wald_test(phonology.model, constraints = constrain_zero(1:3), vcov = V_phonology.model)

#run comparisons between components (i.e. do estimates differ from each other)
Wald_test(phonology.model, constraints = constrain_pairwise(1:3), vcov = V_phonology.model)
```

# Modelling - Literacy

## Model with synthesised effect sizes

```{r echo = T}

agg.Data.lit <- MAc::agg(id = Study, r = Cor, n = N, cor = .5, mod=NULL, data = Data_literacy)
agg.Data.lit <- escalc(measure = "ZCOR", ri = r, ni = n, data = agg.Data.lit)

#add details
agg.Data.lit <- as.data.frame(list(agg.Data.lit, study.details) %>% reduce(left_join, by = c("id"))) 

### fit fixed-effects model
res_lit <- rma(yi, vi, data= agg.Data.lit)
print(res_lit)

predict(res_lit, digits=3, transf=transf.ztor)
```

### Forest plots

```{r echo = T}

pdf(file= "My_MA.lit.pdf", width=20, height=8)

# back-transform the results to correlations and obtain the prediction interval
predict(res_lit, transf=transf.ztor, digits=2)

# draw forest plot
forest(res_lit, header=TRUE, atransf=transf.ztor, order="obs", xlim=c(-1.2, .9),
       at=transf.rtoz(seq(-0.5,0.5,by=0.1)), refline=coef(res_lit), ilab=cbind(agg.Data.lit$Study, agg.Data.lit$Year),  ilab.xpos=c(-1,-.8), cex=.75)
text(c(-1.2, .9), c("Author(s)", "Year"))

dev.off()

```

## Sensitivity analysis - Model with synthesised effect sizes for various correlation sizes

```{r echo = T}

#combine effect sizes with different correlation sizes

compute_rma <- function(cor, Study, Cor, N, Data) {
  d <- MAc::agg(id = Study, r = Cor, n = N, cor = cor, mod=NULL, data = Data_literacy)
  d <- escalc(measure = "ZCOR", ri = r, ni = n, data = d)
  rma(yi, vi, data= d, measure="OR", method="REML")
}

results = list()
for (cor in  seq(.1, 1,.2)) {
    results[[as.character(cor)]] = compute_rma(cor, Study, Cor, N, Data)
  }

print(results)
```

## Diagnostic

### Funnel plots

```{r echo = T}

### set up 2x2 array for plotting
par(mfrow=c(2,2))

### draw funnel plots
funnel(res_lit, main="Standard Error")
funnel(res_lit, yaxis="vi", main="Sampling Variance")
funnel(res_lit, yaxis="seinv", main="Inverse Standard Error")
funnel(res_lit, yaxis="vinv", main="Inverse Sampling Variance")

dev.off()

```

```{r contour lit}

### funnel plot
png("funnel.lit..png",bg = "white", width = 1024, height = 768)
funnel(res_lit, xlab = "Correlation coefficient")
dev.off()

### create contour enhanced funnel plot (with funnel centered at 0)
png("funnel.lit.colour.png",bg = "white", width = 1024, height = 768)
funnel(res_lit, level=c(90, 95, 99), shade=c("white", "orange", "red"), refline=0, legend = TRUE)
dev.off()
```

### PET - PEESE

```{r echo = T}

regtest(res_lit)
regtest(res_lit, predictor="vi") # PEESE

```

### Ranktest

```{r echo = T}

ranktest(res_lit, exact = FALSE)
```

### Outlier/influential points detection

```{r echo = T}

### calculate influence diagnostics
inf_lit <- influence(res_lit)
 
### plot the influence diagnostics
plot(inf_lit)
```

## Literacy Model with dependencies

```{r echo = T}

# Overall model with dependencies: general model

intercept.lit.model <- robu(formula = yi ~ 1, data = Data_literacy,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)

print(intercept.lit.model)
sensitivity(intercept.lit.model)
```

### Forest plot

```{r eval = F}

pdf(file = "forestplot_lit.pdf", width = 20, height = 28, pointsize = 8)

forest.robu(intercept.lit.model, es.lab = "Component", study.lab = "Study", "Effect Size" = yi)

dev.off()
```

### Diagnostic

#### Egger's regression test/ PET-PEESE procedure

```{r echo = T}

# with un-corrected ES (PET) - use standard error as predictor
PET_lit <- robu(formula = yi ~ sei, data = Data_literacy,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(PET_lit)

# with un-corrected ES (PEESE) - use variance as predictor
PEESE_lit <- robu(formula = yi ~ vi, data = Data_literacy,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(PEESE_lit)

```

### Moderators {.tabset}

#### Literacy model - Group as predictor

```{r echo = T}

lit.group <- robu(formula = yi ~ 0 + Group, data = Data_literacy, studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lit.group)
sensitivity(lit.group)

#test overall component effect (i.e. do estimates differ from zero)
Wald_test(lit.group, constraints = matrix(c(1,0,0,0,1,0,0,0,1),3,3), vcov = "CR2")

#run comparisons between groups (i.e. do estimates differ from each other)
V_lit.group <- vcovCR(lit.group, type = "CR2")
Wald_test(lit.group, constraints = constrain_equal(1:3), vcov = V_lit.group)
```

#### Literacy model - Component as predictor

```{r echo = T}

# Overall model with dependencies: general model
table(Data_literacy$Component, Data_literacy$Variable)

lit.component <- robu(formula = yi ~ 0 + Component, data = Data_literacy[Data_literacy$Component == 'Reading'| Data_literacy$Component == "Spelling",], studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lit.component)
sensitivity(lit.component)

#test overall component effect (i.e. do estimates differ from zero)
Wald_test(lit.component, constraints = matrix(c(1,0,0,1),2,2), vcov = "CR2")

#run comparisons between components (i.e. do estimates differ from each other)
V_lit.component <- vcovCR(lit.component, type = "CR2")
Wald_test(lit.component, constraints = constrain_equal(1:2), vcov = V_lit.component)
```

#### Literacy model - Age

```{r echo = T}
# Overall model with dependencies: general model


lit.age <- robu(formula = yi ~ Age, data = Data_literacy,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lit.age)
sensitivity(lit.age)
```

#### Literacy model - Sequence complexity

```{r echo = T}
# Overall model with dependencies: general model

lit.seq.complexity <- robu(formula = yi ~ -1 + as.factor(Seq_complexity), data = Data_literacy[Data_literacy$Seq_complexity == "FOC" | Data_literacy$Seq_complexity == "SOC", ],
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)

print(lit.seq.complexity)
sensitivity(lit.seq.complexity)

#test overall sequence complexity effect (i.e. do estimates differ from zero)
Wald_test(lit.seq.complexity, constraints = matrix(c(1,0,0,1),2,2), vcov = "CR2", tidy = TRUE)

#run pairwise comparisons between sequence complexity  (i.e. do estimates differ from each other)
Wald_test(lit.seq.complexity, constraints = constrain_equal(c(1,2)), vcov = "CR2", tidy = TRUE)

```

#### Literacy model - Session

```{r echo = T}
# Overall model with dependencies: general model

table(Data_literacy$Time, Data_literacy$Variable) # third session is removed as there are not enough effect sizes

lit.session <- robu(formula = yi ~ Time-1, data = Data_literacy[Data_literacy$Time != 3,],
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lit.session)
sensitivity(lit.session)

#test overall session effect (i.e. do estimates differ from zero)
Wald_test(lit.session, constraints = matrix(c(1,0,0,1),2,2), vcov = "CR2", tidy = TRUE)

#run pairwise comparisons between sessions (i.e. do estimates differ from each other)
Wald_test(lit.session, constraints = constrain_equal(1:2), vcov = "CR2", tidy = TRUE)
```

#### Literacy model - number of trials

```{r echo = T}
# Overall model with dependencies: general model


lit.trials <- robu(formula = yi ~ Trial_no, data = Data_literacy,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lit.trials)
sensitivity(lit.trials)
```

#### Literacy model - Type of sequence

```{r echo = T}
# Overall model with dependencies: general model

lit.seq.type <- robu(formula = yi ~ -1 + as.factor(Seq_type), data = Data_literacy,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(lit.seq.type)
sensitivity(lit.seq.type)

#test overall SRT type effect (is the estimate for each group different from zero)
Wald_test(lit.seq.type, constraints = matrix(c(1,0,0,0,1,0,0,0,1),3,3), vcov = "CR2", tidy = TRUE)

#run comparisons between types of sequence (are the estimates difference from each other)
V_lit.seq.type <- vcovCR(lit.seq.type, type = "CR2")
Wald_test(lit.seq.type, constraints = constrain_equal(1:2), vcov = V_lit.seq.type)
```

### Literacy components - comparison between groups {.tabset}

#### reading model - group as predictor

```{r echo = T}

table(Data_reading$Group, Data_reading$Component)

reading.model <- robu(formula = yi ~ 0 + Group, data = Data_reading,
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)
print(reading.model)
sensitivity(reading.model)

#test overall group effect (i.e. do estimates differ from zero)
Wald_test(reading.model, constraints = matrix(c(1,0,0,0,1,0,0,0,1),3,3), vcov = "CR2",tidy = TRUE)

#run pairwise comparisons between groups (i.e. do estimates differ from each other)
V_reading.model <- vcovCR(reading.model, type = "CR2") 
Wald_test(reading.model, constraints = constrain_pairwise(1:3), vcov = V_reading.model)
```

#### spelling model - group as predictor

```{r echo = T}

table(Data_spelling$Group, Data_spelling$Component)

spelling.model <- robu(formula = yi ~ 0 + Group, data = Data_spelling[Data_spelling$Group != 'DLD',],
                       studynum = Study, var.eff.size = vi,
                       rho = .8, small = TRUE)

print(spelling.model)
sensitivity(spelling.model)

#test overall component effect (i.e. do estimates differ from zero)
Wald_test(spelling.model, constraints = matrix(c(1,0,0,1),2,2), vcov = "CR2",tidy = TRUE)

#run pairwise comparisons between components (i.e. do estimates differ from each other)
Wald_test(spelling.model, constraints = constrain_equal(1:2), vcov = "CR2", tidy = TRUE)
```

```{r}
#stargazer(g, z,  type="html", out="models.htm")
```

# Summary table

Disattenuation using Spearman's formula [@spearman1904]

```{r}
#res.table <- read_excel("subgroup analysis - correlational meta.xlsx")

#res.table$r <-  apply(res.table["z'"], 1, function(x) ztor(x))

#rxx <- 0.3095069
#res.table$R <-  apply(res.table["r"], 1, function(x) Disat(x, rxx))

#write.csv(res.table, "MA.table.csv")
```

# Session information

sessionInfo()

